A Type System for String Sanitation\\Implemented Inside a Python

### 2014-04-16 sanitation-plas14/sanitation-plas14.tex
Removed val judgements.

\newcommand{\val}{ \ {\tt val} }
\newcommand{\ival}{ \ {\tt ival} }

@@

This section presents the grammar and semantics of $\lcs$.
The semantics are defined in terms of an internal language with at least strings and a regex filter function.
These constraints are captured by the internal term valuations ($\ival$).
The internal language does not necessarily need a regex filter function because
any dynamic conversion is easily definable using a combination of filters and safe
casting.

@@

\begin{figure}
\begin{center}
\begin{tabular}{c r}
\inferline{Te-Include}
{\strin{s} \val}
{ \cdot }

\inferline{S-E-Concat}
{\siconcat{S_1}{S_2} \ereduces \strin{s_1 \cdot s_2}} % ???
{S_1 \Downarrow \strin{s_1} \\ S_2 \Downarrow \strin{s_2}}

\inferline{S-E-Subst}
{\sisubst{r}{S_1}{S_2} \ereduces s}
{S_1 \Downarrow \strin{s_1} \\ S_2 \Downarrow \strin{s_2} \\ \dosubst{r}{s_1}{s_2} = s}

\inferline{S-E-Coerce-OK}
{\coerce{r}{S} \ereduces \strin{s}}
{S \ereduces \strin{s} \\ x \in \lang{r}}

\inferline{S-E-Coerce-NotOk}
{S \err}
{\coerce{r}{S} \ereduces \strin{s} \\ s \not \in \lang{r}}

@@

\begin{thm}[Main Soundness Result]
  If $\cdot \vdash e : \strin{r} \sreduces i$ then either $i \treduces \err$ or
  if $i \sreduces v$ for $v \ival$ then $v \in r$.
\end{thm}

>>>>

@@

This section presents the grammar and semantics of $\lcs$.
The semantics are defined in terms of an internal language with at least strings and a regex filter function.
These constraints are captured by the internal term valuations.
The internal language does not necessarily need a regex filter function because
any dynamic conversion is easily definable using a combination of filters and safe
casting.

@@

\begin{figure}
\begin{center}
\begin{tabular}{c r}
\inferline{S-E-Include}
{\strin{s} \sreduces \strin{s}}
{ \cdot }

\inferline{S-E-Concat}
{\siconcat{S_1}{S_2} \sreduces \strin{s_1 \cdot s_2}} % ???
{S_1 \sreduces \strin{s_1} \\ S_2 \sreduces \strin{s_2}}

\inferline{S-E-Subst}
{\sisubst{r}{S_1}{S_2} \sreduces s}
{S_1 \sreduces \strin{s_1} \\ S_2 \sreduces \strin{s_2} \\ \dosubst{r}{s_1}{s_2} = s}

\inferline{S-E-Coerce-OK}
{\coerce{r}{S} \sreduces \strin{s}}
{S \sreduces \strin{s} \\ x \in \lang{r}}

\inferline{S-E-Coerce-NotOk}
{S \err}
{\coerce{r}{S} \sreduces \strin{s} \\ s \not \in \lang{r}}

@@

\begin{thm}[Main Soundness Result]
  If $\cdot \vdash e : \strin{r} \sreduces i$ then either $i \treduces \err$ or
  if $i \sreduces v$ for $v$??? then $v \in r$.
\end{thm}
